Final Project Data 205

### 2021-12-15 Draft Final Project1.Rmd
Add files via upload

```{r}
WMATA$year<-as.numeric(format(WMATA$date,"%Y"))
head(WMATA)
```

@@

```{r}
#Create a time series plot
WMATA$hour <- as.numeric(gsub(":.*$", "", WMATA$time))
WMATA$timeofday <- ifelse(WMATA$hour >= 5 & WMATA$hour<=11, "morning",
                            ifelse(WMATA$hour > 11 & WMATA$hour<=16, "afternoon",
                            ifelse(WMATA$hour >16 & WMATA$hour <=19, "evening", "night"))) 
WMATA
```

@@

## Plot Types of Crime
```{r}
p2<-WMATA  %>%
  filter(type %in% c("ARREST","REPORT","SUMMONS/CITATION")) %>%
  ggplot(aes(x=type, fill= type))+
  geom_bar()+
  labs(title="Classification of Type of Crime/ Reporting",x="Type", y="Total")+
  scale_fill_brewer(palette = "Blues") + theme_minimal()
p2 + theme_minimal()
```

@@

## Facet
```{r}
 ggplot(data = d4,
        mapping = aes(x = year, y = Freq)) +
     geom_bar(stat="identity") +
     facet_wrap(vars(timeofday)) +
     theme_minimal()
```

##Prepare the Data
```{r}
DMV<-WMATA %>%
  select(type,year)%>%
  filter(year >=2017  & type %in% c("ARREST","REPORT","SUMMONS/CITATION"))%>%
  group_by(year)
```

```{r}
head(DMV)
```

## using count 
```{r}
WMATA %>%
  group_by(year,timeofday) %>%
  summarise(n = n()) %>%
  mutate(Freq = n/sum(n))
```

## Time Series

```{r}
sp <- ggplot(WMATA, aes(x=year, )) + geom_point(shape=1)
sp + facet_grid(. ~ cat)
```
##
```{r}
hp <- ggplot(tips, aes(x=total_bill)) + geom_histogram(binwidth=2,colour="white")
```

## Getting the WMATA Geocodes
```{r}
library(dplyr)
library(stringr)
library(tidygeocoder)

@@

#Apply the geocode function to get lat/lon values
coordinates <- df_md %>% geocode(full_addr)
```

>>>>

```{r}
WMATA$year<-as.numeric(format(WMATA$date,"%Y"))
WMATA$month<-as.numeric(format(WMATA$date,"%m"))
head(WMATA)
```

@@

```{r}
#Create a time series plot
WMATA$hour <- as.numeric(gsub(":.*$", "", WMATA$time))
WMATA$timeofday <- ifelse(WMATA$hour >= 5 & WMATA$hour<=11, "Morning",
                            ifelse(WMATA$hour > 11 & WMATA$hour<=16, "Afternoon",
                            ifelse(WMATA$hour >16 & WMATA$hour <=19, "Evening", "Night"))) 
WMATA
```

@@

## Plot Types of Crime
```{r}
p2<-WMATA  %>%
  filter(type %in% c("ARREST","REPORT","SUMMONS/CITATION")) %>%
  ggplot(aes(x=type, fill= type))+
  geom_bar()+
  labs(title="Classification of Type of Crime/ Reporting",x="Type", y="Total")+
  scale_fill_brewer(palette = "") + theme_minimal()
p2 + theme_minimal()
```

@@

## Facet
```{r}
 ggplot(data = d4,
        mapping = aes(x = year, y = Freq, fill=timeofday)) +
     geom_bar(stat="identity") +
     facet_wrap(vars(timeofday)) +
      scale_fill_brewer(palette = "Spectral") +
     theme_minimal()

##Prepare the Data
```{r}
DMV<-WMATA %>%
  select(type,year)%>%
  group_by(year, type)%>%
  filter(year >=2017  & type %in% c("ARREST","REPORT","SUMMONS/CITATION"))%>%
  dplyr::summarize(Freq=n())
```

```{r}
head(DMV)
```
```{r}
ggplot(data = DMV,
      mapping = aes(x = year, y = Freq)) +
     geom_line(stat="identity") +
     facet_wrap(vars(type)) +
     scale_fill_brewer(palette = "Spectral") +
     theme_minimal()
```

## Months & Count
```{r}
DF6<- WMATA%>%
  group_by(month) %>%
  dplyr::summarize(count=n())
DF6
```

```{r}
df7<-na.omit(DF6)
```

## Time Series 
```{r}
P6<- ggplot(df7, aes(x=month, fill=month)) + 
  geom_bar(stat="identity", color="black", 
           position=position_dodge()) +
  geom_errorbar(aes(ymin=len-sd, ymax=len+sd), width=.2,
                 position=position_dodge(.9))
```

## Getting the WMATA Geocodes
```{r}
library(dplyr)
library(httr)
#library(jsonlite)
library(stringr)
library(tidygeocoder)

@@

#Filter on just Maryland addresses
df_md <- df_wmata2 %>% filter(state=="MD")
```

```{r}
#Apply the geocode function to get lat/lon values
coordinates <- df_md %>% geocode(full_addr, method="arcgis")

coordinates$census_tract <- 0
row_count <- nrow(coordinates)

# Get FIPS code from FCC API based on lat/lon
fcc_url = "https://geo.fcc.gov/api/census/block/find?"
headers = "'Content-Type':'application/json'"
unique_record = 0

for (row in 1:row_count) {
  if (!is.na(coordinates$lat[row]) & coordinates$time[row] != unique_record) {

    full_url <- paste0(fcc_url, "latitude=", coordinates$lat[row],
                       "&longitude=", coordinates$long[row], "&censusYear=2010&format=json")
    fcc <- GET(full_url)
    fcc_parsed <- content(fcc, as="parsed")
    try(coordinates$census_tract[row] <- fcc_parsed$Block$FIPS, TRUE)

    print(full_url)
    print(coordinates$census_tract[row])
    unique_record = coordinates$time[row]
  }
  Sys.sleep(1)
}

census_info <- GET("https://api.census.gov/data/2019/acs/acs5?get=NAME,B01003_001E,B02001_002E,B02001_003E&for=block%20group:*&in=state:24&in=county:031&in=tract:*")
df_census <- fromJSON(content(census_info, as="text"))

df_census
```
